Local to global N input modelling

### 2025-06-09 manuscript.qmd
Updates

```{r fig-farm-mean-temps}
#| fig-cap: |
#|   Potential options for showing farm site mean temperatures. Top left: Mean temperature by latitude across countries. Top right: Frequency distribution of mean temperatures by hemisphere. Bottom: global distribution of mean temperatures.
#| fig-height: 9
#| fig-width: 9.5

@@

worldmap <- ne_countries(scale = "large", returnclass = "sf")
p1 <- ggplot() +
  geom_sf(data = worldmap, fill = "white", color = "dimgray") +
  geom_sf(data = farm_temp_means, aes(color = mean_temp, geometry = geometry), size = 1) +
  coord_sf() +
  scale_color_viridis_c(option = "turbo") +
  guides(col = guide_colourbar(
    title = "Mean temperature (°C)",
    direction = "vertical", position = "right",
    label.position = "right", title.position = "top", 
    title.vjust = 1, title.hjust = 0.5,
    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 2,
    barwidth = 1.5, barheight = 20
  )) +
  prettyplot() +
  labs(y = "Latitude", x = "Longitude")

p_Can1 <- p1 + 
  coord_sf(xlim = inset_boxes_sm[["CAN1"]][["xlims"]], 
           ylim = inset_boxes_sm[["CAN1"]][["ylims"]])  +
  draw_label("A", size = 14, fontface = "bold", 
             x = inset_boxes_sm[["CAN1"]][["labx"]], 
             y = inset_boxes_sm[["CAN1"]][["laby"]], 
             hjust = -1, vjust = 0.5)
p_Can2 <- p1 + 
  coord_sf(xlim = inset_boxes_sm[["CAN2"]][["xlims"]], 
           ylim = inset_boxes_sm[["CAN2"]][["ylims"]])  +
  draw_label("B", size = 14, fontface = "bold", 
             x = inset_boxes_sm[["CAN2"]][["labx"]], 
             y = inset_boxes_sm[["CAN2"]][["laby"]], 
             hjust = 0.5, vjust = 0)
p_Eur <- p1 + 
  coord_sf(xlim = inset_boxes_sm[["EUR"]][["xlims"]], 
           ylim = inset_boxes_sm[["EUR"]][["ylims"]])  +
  draw_label("C", size = 14, fontface = "bold", 
             x = inset_boxes_sm[["EUR"]][["labx"]], 
             y = inset_boxes_sm[["EUR"]][["laby"]], 
             hjust = -1, vjust = 0.5)
p_Chi <- p1 + 
  coord_sf(xlim = inset_boxes_sm[["CHI"]][["xlims"]], 
           ylim = inset_boxes_sm[["CHI"]][["ylims"]])  +
  theme(legend.position = "right") +
  draw_label("D", size = 14, fontface = "bold", 
             x = inset_boxes_sm[["CHI"]][["labx"]], 
             y = inset_boxes_sm[["CHI"]][["laby"]], 
             hjust = 0, vjust = 0)
p_Aus <- p1 + 
  coord_sf(xlim = inset_boxes_sm[["AUS"]][["xlims"]], 
           ylim = inset_boxes_sm[["AUS"]][["ylims"]])  +
  draw_label("E", size = 14, fontface = "bold", 
             x = inset_boxes_sm[["AUS"]][["labx"]], 
             y = inset_boxes_sm[["AUS"]][["laby"]], 
             hjust = 0, vjust = 0)

@@

```{r fig-biomass-variation, class.chunk = "aside"}
plot(coho_biom_summ$temp_c, coho_biom_summ$perc_diff)
plot(coho_biom_summ$tonnes_per_farm, coho_biom_summ$perc_diff)
```

@@

Total uneaten feed across a cohort (548 days) fed the reference feed ranged from 
`r uneaten_total_stats$min[uneaten_total_stats$feed == "reference"]` to 
`r uneaten_total_stats$max[uneaten_total_stats$feed == "reference"]` g kg$^{-1}$ fish, with a mean of 
`r uneaten_total_stats$mean[uneaten_total_stats$feed == "reference"]` g kg$^{-1}$ fish.

* Differences between the feeds were very small, with the past scenario producing 
* but slightly less uneaten feed was lost in the reference scenario. Uneaten past feed ranged from 
`r uneaten_total_stats$min[uneaten_total_stats$feed == "past"]` to `r uneaten_total_stats$min[uneaten_total_stats$feed == "past"]` g kg$^{-1}$ (mean of `r uneaten_total_stats$mean[uneaten_total_stats$feed == "past"]`) while uneaten future feed ranged from 
`r uneaten_total_stats$min[uneaten_total_stats$feed == "future"]` to `r uneaten_total_stats$min[uneaten_total_stats$feed == "future"]` g kg$^{-1}$ (mean of `r uneaten_total_stats$mean[uneaten_total_stats$feed == "future"]`).
* @fig-total-uneaten-perday shows the range of total uneaten feed per day across countries.

```{r fig-total-uneaten-perday}
#| fig-width: 9.5

@@

* The composition of the uneaten feed is (obviously) the same as the total feed composition (@sec-feeds).

@@

* Total reference excreted faeces across a cohort (548 days) ranged from `r excreted_total_stats$min[excreted_total_stats$feed == "reference"]` to `r excreted_total_stats$max[excreted_total_stats$feed == "reference"]` g kg$^{-1}$, with a mean of `r excreted_total_stats$mean[excreted_total_stats$feed == "reference"]`.
* There was very little difference between the past and future feeds and the reference feed. Uneaten past feed ranged from 
`r excreted_total_stats$min[excreted_total_stats$feed == "past"]` to `r excreted_total_stats$max[excreted_total_stats$feed == "past"]` g kg$^{-1}$ (mean of `r excreted_total_stats$mean[excreted_total_stats$feed == "past"]` g kg$^{-1}$) while uneaten future feed ranged from 
`r excreted_total_stats$min[excreted_total_stats$feed == "future"]` to `r excreted_total_stats$max[excreted_total_stats$feed == "future"]` g kg$^{-1}$ (mean of `r excreted_total_stats$mean[excreted_total_stats$feed == "future"]` g kg$^{-1}$).
* @fig-total-excreted-perday shows the range of total excreted faeces per day across countries.

```{r fig-total-excreted-perday}
#| fig-width: 9

@@

```{r fig-total-excr-diff_perc, class.chunk = "aside"}
#| fig-cap: Mean % difference in excreted faeces of the two experimental feeds (compared to the reference feed) with increasing overall excretion.

@@

df %>% 
  ggplot(aes(x = reference, y = diff_perc, colour = hemisphere)) +
  geom_point() + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  facet_grid(~feed) +
  prettyplot()
```

The difference in total excretion for the past feed ranged from 
`r summ$min[summ$feed == "past"]`-`r summ$max[summ$feed == "past"]`% across all farms globally, and for the future feed ranged from 
`r summ$min[summ$feed == "future"]`-`r summ$max[summ$feed == "future"]`%.

```{r fig-total-excr-diff_perc_2, class.chunk = "aside"}
#| fig-cap: Mean % difference in excreted faeces of the two experimental feeds (compared to the reference feed) over time in one production cycle.

@@

```{r fig-total-excr-act_diff}
#| fig-width: 6.25
#| fig-height: 5.25
#| fig-cap: Mean actual difference in excreted faeces of the two experimental feeds (compared to the reference feed) over time in one production cycle.

@@

# Supplementary stuff

@@

Looking at @fig-param-sens-weight:

* The most sensitive parameter by far is $m$ (the weight exponent for anabolism), followed closely by $n$ the (weight exponent for catabolism)
* These two are also relatively uncertain, as $m$ was taken from *Salmo trutta* measurements in a fairly old paper [@broekhuizen_modelling_1994] and $n$ was taken from @baldan_r_2018 which did not specifically look at Atlantic salmon.

>>>>

```{r fig-farm-mean-temps}
#| fig-cap: |
#|   Potential options for showing data spatially. Top left: Mean temperature by latitude across countries. Top right: Frequency distribution of mean temperatures by hemisphere. Bottom: global distribution of mean temperatures.
#| fig-height: 9
#| fig-width: 9.5

@@

worldmap <- ne_countries(scale = "large", returnclass = "sf")
p1 <- ggplot() +
  geom_sf(data = worldmap, fill = "white", color = "dimgray") +
  geom_sf(data = farm_temp_means, aes(color = mean_temp, geometry = geometry), size = 2) +
  coord_sf() +
  scale_color_viridis_c(option = "turbo") +
  guides(col = guide_colourbar(
    title = "Mean temperature (°C)",
    direction = "vertical", position = "right",
    label.position = "right", title.position = "top", 
    title.vjust = 1, title.hjust = 0.5,
    frame.colour = "black", ticks.colour = "black",ticks.linewidth = 2,
    barwidth = 1.5, barheight = 20
  )) +
  prettyplot() +
  labs(y = "Latitude", x = "Longitude")

p_Can1 <- p1 + 
  coord_sf(xlim = inset_boxes_sm[["CAN1"]][["xlims"]], 
           ylim = inset_boxes_sm[["CAN1"]][["ylims"]])  +
  draw_label("A", size = 14, fontface = "bold", 
             x = inset_boxes_sm[["CAN1"]][["labx"]], 
             y = inset_boxes_sm[["CAN1"]][["laby"]], 
             hjust = -1, vjust = 0.5)
p_Can2 <- p1 + 
  coord_sf(xlim = inset_boxes_sm[["CAN2"]][["xlims"]], 
           ylim = inset_boxes_sm[["CAN2"]][["ylims"]])  +
  draw_label("B", size = 14, fontface = "bold", 
             x = inset_boxes_sm[["CAN2"]][["labx"]], 
             y = inset_boxes_sm[["CAN2"]][["laby"]], 
             hjust = 0.5, vjust = 0.5)
p_Eur <- p1 + 
  coord_sf(xlim = inset_boxes_sm[["EUR"]][["xlims"]], 
           ylim = inset_boxes_sm[["EUR"]][["ylims"]])  +
  draw_label("C", size = 14, fontface = "bold", 
             x = inset_boxes_sm[["EUR"]][["labx"]], 
             y = inset_boxes_sm[["EUR"]][["laby"]], 
             hjust = -1, vjust = 0.5)
p_Chi <- p1 + 
  coord_sf(xlim = inset_boxes_sm[["CHI"]][["xlims"]], 
           ylim = inset_boxes_sm[["CHI"]][["ylims"]])  +
  theme(legend.position = "right") +
  draw_label("D", size = 14, fontface = "bold", 
             x = inset_boxes_sm[["CHI"]][["labx"]], 
             y = inset_boxes_sm[["CHI"]][["laby"]], 
             hjust = 0, vjust = 0)
p_Aus <- p1 + 
  coord_sf(xlim = inset_boxes_sm[["AUS"]][["xlims"]], 
           ylim = inset_boxes_sm[["AUS"]][["ylims"]])  +
  draw_label("E", size = 14, fontface = "bold", 
             x = inset_boxes_sm[["AUS"]][["labx"]], 
             y = inset_boxes_sm[["AUS"]][["laby"]], 
             hjust = 0, vjust = 0.5)

@@

```{r fig-biomass-variation, class.chunk = "aside"}
plot(coho_biom_summ$temp_c, coho_biom_summ$perc_diff)
# plot(coho_biom_summ$tonnes_per_farm, coho_biom_summ$perc_diff)
```

@@

Total uneaten feed across a cohort (548 days) fed the reference feed ranged from 
`r uneaten_total_stats$min[uneaten_total_stats$feed == "reference"]` to 
`r uneaten_total_stats$max[uneaten_total_stats$feed == "reference"]` g kg$^{-1}$ fish, with a mean of 
`r uneaten_total_stats$mean[uneaten_total_stats$feed == "reference"]` g kg$^{-1}$ fish. 
Differences between the feeds were very small, but slightly less feed was left uneaten in the reference scenario (@fig-total-uneaten-perday). Uneaten feed in the past scenario ranged from 
`r uneaten_total_stats$min[uneaten_total_stats$feed == "past"]` to 
`r uneaten_total_stats$max[uneaten_total_stats$feed == "past"]` g kg$^{-1}$ fish (mean of 
`r uneaten_total_stats$mean[uneaten_total_stats$feed == "past"]` g kg$^{-1}$ fish) while uneaten feed in the future scenario ranged from 
`r uneaten_total_stats$min[uneaten_total_stats$feed == "future"]` to 
`r uneaten_total_stats$max[uneaten_total_stats$feed == "future"]` g kg$^{-1}$ (mean of 
`r uneaten_total_stats$mean[uneaten_total_stats$feed == "future"]`  g kg$^{-1}$ fish).

```{r fig-total-uneaten-perday}
#| fig-cap: |
#|   Feed left uneaten when fish are fed the reference (blue), past (red) or future (green) feed. Countries are arranged by descending mean latitude.

@@

The composition of the uneaten feed is (obviously) the same as the total feed composition detailed in (@sec-feeds).

@@

Overall, total excretion was lowest when when fish were fed the past feed and highest when fish were fed the reference feed (@fig-total-excreted-perday). 
Total excreted faeces across a cohort (548 days) in the reference scenario ranged from `r excreted_total_stats$min[excreted_total_stats$feed == "reference"]` to 
`r excreted_total_stats$max[excreted_total_stats$feed == "reference"]` g kg$^{-1}$ fish d$^{-1}$, with a mean of 
`r excreted_total_stats$mean[excreted_total_stats$feed == "reference"]`.
Total excreted faeces across a cohort in the past scenario ranged from 
`r excreted_total_stats$min[excreted_total_stats$feed == "past"]` to 
`r excreted_total_stats$max[excreted_total_stats$feed == "past"]` g kg$^{-1}$ fish d$^{-1}$ (mean of 
`r excreted_total_stats$mean[excreted_total_stats$feed == "past"]` g kg$^{-1}$ fish d$^{-1}$).
Total excreted faeces across a cohort in the future scenario ranged from 
`r excreted_total_stats$min[excreted_total_stats$feed == "future"]` to 
`r excreted_total_stats$max[excreted_total_stats$feed == "future"]` g kg$^{-1}$ fish d$^{-1}$ (mean of 
`r excreted_total_stats$mean[excreted_total_stats$feed == "future"]` g kg$^{-1}$ fish d$^{-1}$).

```{r fig-total-excreted-perday}
#| fig-cap: |
#|   Feed left uneaten when fish are fed the reference (blue), past (red) or future (green) feed. Countries are arranged by descending mean latitude.

@@

```{r fig-total-excr-diff_perc, class.chunk = "aside"}
#| eval: false
#| fig-cap: |
#|   Mean % difference in excreted faeces of the two experimental feeds (compared to the reference feed) with increasing overall excretion.

@@

df %>% 
  ggplot(aes(x = reference, y = diff_perc, colour = hemisphere)) +
  geom_point() + 
  geom_hline(yintercept = 0, linetype = "dashed") +
  facet_grid(~feed) +
  prettyplot()

# The difference in total excretion for the past feed ranged from 
# `r summ$min[summ$feed == "past"]`-`r summ$max[summ$feed == "past"]`% across all farms globally, and for the future feed ranged from 
# `r summ$min[summ$feed == "future"]`-`r summ$max[summ$feed == "future"]`%. 
```

```{r fig-total-excr-diff_perc_2, class.chunk = "aside"}
#| eval: false
#| fig-cap: |
#|   Mean % difference in excreted faeces of the two experimental feeds (compared to the reference feed) over time in one production cycle.

@@

```{r fig-total-excr-act_diff}
#| eval: false
#| fig-width: 6.25
#| fig-height: 5.25
#| fig-cap: Mean actual difference in excreted faeces of the two experimental feeds (compared to the reference feed) over time in one production cycle.

@@

# Supplementary materials

@@

The most sensitive parameter by far in @fig-param-sens-weight is $m$ (the weight exponent for anabolism), followed closely by $n$ the (weight exponent for catabolism). 
These two are also relatively uncertain, as $m$ was taken from *Salmo trutta* measurements in a fairly old paper [@broekhuizen_modelling_1994] and $n$ was taken from @baldan_r_2018 which did not specifically look at Atlantic salmon.
